The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multi-Phase Forest Inventories

### 2017-10-06 JStatSoft_forestinventory_master-concordance.tex
merge twophase 3

\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:%
1 107 1 1 4 1 1 1 4 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Introduction.Rnw:ofs 115:%
1 97 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 213:%
123 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Main structure and modules of the Package.Rnw:ofs 223:%
1 71 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 295:%
134 11 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Twophase_Estimators and their Application.Rnw:ofs 307:%
1 132 1 1 4 1 1 1 2 1 0 2 1 3 0 1 2 2 1 1 3 14 0 1 2 16 1 1 5 7 0 1 2 4 1 1 2 24 0 1 2 6 1 1 2 4 0 1 2 4 1 1 2 1 0 1 5 6 0 1 2 3 1 1 2 8 0 1 2 129 1 1 7 6 0 1 1 26 0 1 2 3 1 1 2 13 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 7 1 1 6 5 0 1 1 8 0 1 2 7 1 1 2 4 0 1 2 1 1 1 6 5 0 1 1 3 0 1 2 1 1 1 2 11 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 848:%
147}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Threephase_Estimators and their Application.Rnw:ofs 849:%
1 102 1 1 2 1 0 1 1 3 0 1 2 4 1 1 4 1 1 1 6 8 0 1 2 2 1 1 2 27 0 1 2 169 1 1 3 2 0 1 1 3 0 1 2 4 1 1 8 10 0 1 2 1 1 1 4 1 1 1 2 12 0 1 2 4 1 1 7 9 0 1 2 2 1 1 2 12 0 1 2 6 1 1 7 9 0 1 2 2 1 1 2 12 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1284:%
149 11 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Calculation of Confidence Intervals.Rnw:ofs 1296:%
1 42 1 1 2 11 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1361:%
162 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Special Cases and Scenarios.Rnw:ofs 1371:%
1 20 1 1 2 4 0 1 2 4 1 1 6 8 0 1 2 4 1 1 6 8 0 1 2 18 1 1 8 16 1 1 7 9 0 1 2 2 1 1 2 8 0 1 2 2 1 1 2 8 0 1 2 21 1 1 3 5 0 1 2 28 1 1 3 5 0 1 2 40 1 1 3 5 0 1 2 25 1 1 3 5 0 1 2 19 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1657:%
173 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Analysis and Visualization.Rnw:ofs 1667:%
1 20 1 1 4 6 0 1 2 3 1 1 6 8 0 1 2 2 1 1 7 9 0 1 2 2 1 1 7 9 0 1 2 2 1 1 8 10 0 1 2 4 1 1 5 7 0 1 2 6 1 1 2 4 0 1 2 2 1 1 2 26 0 1 2 16 1 1 4 1 1 1 2 11 0 1 2 18 1 1 5 7 0 1 2 4 1 1 3 5 0 1 2 10 1 1 2 4 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1898:%
184 8 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Acknowledgements.Rnw:ofs 1907:%
1 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1912:%
194 11 1}

>>>>

\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:%
1 107 1 1 4 1 1 1 4 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Introduction.Rnw:ofs 115:%
1 97 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 213:%
123 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Main structure and modules of the Package.Rnw:ofs 223:%
1 71 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 295:%
134 11 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Twophase_Estimators and their Application.Rnw:ofs 307:%
1 110 1 1 4 1 1 1 2 1 0 2 1 3 0 1 2 2 1 1 3 14 0 1 2 16 1 1 5 7 0 1 2 4 1 1 2 24 0 1 2 6 1 1 2 4 0 1 2 4 1 1 2 1 0 1 5 6 0 1 2 3 1 1 2 8 0 1 2 126 1 1 7 6 0 1 1 26 0 1 2 3 1 1 2 13 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 7 1 1 6 5 0 1 1 8 0 1 2 7 1 1 2 4 0 1 2 1 1 1 6 5 0 1 1 3 0 1 2 1 1 1 2 11 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 823:%
147}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Threephase_Estimators and their Application.Rnw:ofs 824:%
1 101 1 1 2 1 0 1 1 3 0 1 2 4 1 1 4 1 1 1 6 8 0 1 2 2 1 1 2 27 0 1 2 162 1 1 3 2 0 1 1 3 0 1 2 4 1 1 8 10 0 1 2 1 1 1 4 1 1 1 2 12 0 1 2 4 1 1 7 9 0 1 2 2 1 1 2 12 0 1 2 6 1 1 7 9 0 1 2 2 1 1 2 12 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1251:%
149 11 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Calculation of Confidence Intervals.Rnw:ofs 1263:%
1 42 1 1 2 11 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1328:%
162 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Special Cases and Scenarios.Rnw:ofs 1338:%
1 20 1 1 2 4 0 1 2 4 1 1 6 8 0 1 2 4 1 1 6 8 0 1 2 18 1 1 8 16 1 1 7 9 0 1 2 2 1 1 2 8 0 1 2 2 1 1 2 8 0 1 2 21 1 1 3 5 0 1 2 28 1 1 3 5 0 1 2 40 1 1 3 5 0 1 2 25 1 1 3 5 0 1 2 19 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1624:%
173 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Analysis and Visualization.Rnw:ofs 1634:%
1 20 1 1 4 6 0 1 2 3 1 1 6 8 0 1 2 2 1 1 7 9 0 1 2 2 1 1 7 9 0 1 2 2 1 1 8 10 0 1 2 4 1 1 5 7 0 1 2 6 1 1 2 4 0 1 2 2 1 1 2 26 0 1 2 16 1 1 4 1 1 1 2 11 0 1 2 18 1 1 5 7 0 1 2 4 1 1 3 5 0 1 2 10 1 1 2 4 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1865:%
184 8 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Acknowledgements.Rnw:ofs 1874:%
1 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1879:%
194 11 1}

### 2017-10-06 rnw/Threephase_Estimators and their Application.Rnw
merge twophase 3

Solving the sample based normal equations, the vector of regression coefficients $\hat{\pmb{\alpha}}_{s_2}$ for the \textbf{\textit{reduced model}}, i.e. using the \textit{reduced set of explanatory variables} $\pmb{Z}^{(0)}(x)$ available at $x \in s_0$, and likewise the vector of regression coefficients $\hat{\pmb{\beta}}_{s_2}$ for the \textbf{\textit{full model}}, i.e. using the \textit{full set of explanatory variables} $\pmb{Z}^t(x)=(\pmb{Z}^{(0)t}(x),\pmb{Z}^{(1)t}(x))$ available only at a subset $x \in s_1 \subset s_0$, are derived as

@@

The package allows for the calculation of \textbf{point estimates} under exhaustive and non-exhaustive use of the auxiliary information in the $s_0$ phase. Staying in the internal model approach again ensures the zero mean residual property over $F$.

@@

In the \textit{non-exhaustive case}, the \textit{estimated} means of $\pmb{Z}^{(0)}(x)$ over both the $s_0$ and $s_1$ phase, as well as the \textit{estimated} mean of $\pmb{Z}(x)$ over the $s_1$ phase are calculated according to \ref{meanvalues3pnex}. If the exact mean over $s_0$ is known, the estimated mean $\hat{\bar{\pmb{Z}}}^{(0)}_0$ can simply be replaced by the exact mean $\bar{\pmb{Z}}^{(0)}_0$. Note that in case of applied boundary adjustment (section \ref{sec:twophase_and_appl}), the simple mean is again replaced by the weighted mean analogous to equation \ref{eq:wmeanZ}.

@@

Note that ${R}(x)=Y(x)-\pmb{Z}^t(x)\hat{\beta}_{s_2}$ denotes the residuals of the full model, whereas ${R}_{0}(x)=Y(x)-\pmb{Z}^{(0)t}\hat{\alpha}_{s_2}$ denotes the residuals of the reduced model. The \textbf{external variance} form under linear regression models is defined as

\begin{subequations}\label{eq:extvar_reg3p}
\begin{align}
\hat{\var}(\hat{Y}_{reg3p,ex})&=\frac{1}{n_1}\frac{1}{n_2}\sum_{x\in{s_2}}\hat{R}_{0}^2(x))
+ (1-\frac{n_2}{n_1})\frac{1}{n^2_2}\sum_{x\in{s_2}}\hat{R}^2(x) \label{eq:extvar_reg3p_ex} \\
\hat{\var}_{ext}(\hat{Y}_{reg3p,nex})&=\frac{1}{n_0}\frac{\sum_{x\in{s_0}}(\hat{Y}_0(x)-\hat{\bar{Y}}_0)^2}{n_0-1} 
+\frac{1}{n_1}\frac{1}{n_2-1}\sum_{x\in{s}_2}(\hat{R}_0(x)-\bar{\hat{R_0}})^2 \nonumber\\
&+(1-\frac{n_2}{n_1})\frac{1}{n_2(n_2-1)}\sum_{x\in{s}_2}(\hat{R}(x)-\bar{\hat{R}})^2 \label{eq:extvar_reg3p_nex}
\end{align}
\end{subequations}

@@

The three two-phase small area estimators described in Section \ref{sec:twophase_sae} can also be extended to the three-phase scenario. The general principle thereby stays the same, i.e. the regession coefficients of the reduced and full model and their variance-covariance matrices are calculated on the entire $s_2$ sample according to equations \ref{eq:normequ_redmod}, \ref{eq:normequ_fullmod}, \ref{eq:covar_alpha} and \ref{eq:covar_beta}, and are subsequently used to make predictions for sample locations restricted to small area $G$.

@@

The unbiased \textbf{point estimates} of the \textbf{small} (\textit{small}) and \textbf{pseudo small area estimator} (\textit{psmall}) are calculated by applying the globally derived reduced and full regression model coefficients to the small area means of the explanatory variables, and then correcting for a potential model bias in $G$ by adding the small area mean of the full model residuals, i.e. ${R}_{G}(x)=Y_G(x)-\pmb{Z}_G^t(x)\hat{\beta}_{s_2}$, to the point estimate. The difference between the mean $\hat{\bar{\pmb{Z}}}^{(0)}_{1,G}$ and the more precise or exact mean $\hat{\bar{\pmb{Z}}}^{(0)}_{0,G}$ and $\bar{\pmb{Z}}^{(0)}_{0,G}$ is again considered as a residual term likewise in the global estimation (equation \ref{eq:reg3p_ex} and \ref{eq:reg3p_nex}).

@@

\begin{subequations}\label{eq:pest_3p_small_psmall}
\begin{flalign}
\hat{\var}_{ext}(\hat{Y}_{G,small,3p})&= \frac{1}{n_{1,G}(n_{2,G}-1)}\sum_{x\in{s}_{2,G}}
 (\hat{R}_0(x)-\hat{\bar{R}}_{0,G})^2 + 
 (1-\frac{n_{2,G}}{n_{1,G}})\frac{1}{n_{2,G}(n_{2,G}-1)}\sum_{x\in{s_{2,G}}}(\hat{R}(x)-\bar{\hat{R}}_G)^2 \label{eq:var_3p_reg_small}&\\
\hat{\var}_{ext}(\hat{Y}_{G,psmall,3p})&= \frac{1}{n_{0,G}(n_{0,G}-1)}\sum_{x\in{s_{0,G}}}(\hat{Y}_0(x)-\hat{\bar{Y}}_{0,G})^2 + 
{\frac{1}{n_{1,G}(n_{2,G}-1)}\sum_{x\in{s}_{2,G}}}
 (\hat{R}_0(x)-\bar{\hat{R}}_{0,G})^2 \nonumber &\\
 &+ (1-\frac{n_{2,G}}{n_{1,G}})\frac{1}{n_{2,G}(n_{2,G}-1)}\sum_{x\in{s_{2,G}}}(\hat{R}(x)-\bar{\hat{R}}_G)^2 \label{eq:var_3p_reg_psmall}
\end{flalign}
\end{subequations}

with $\hat{Y}_{0}(x)=\pmb{Z}^{(0)t}(x)\hat{\pmb{\alpha}}_{s_2}$ being the reduced model predictions and $\hat{R}_{0}=Y(x)-\hat{Y}_{0}$ being the reduced model residuals. Likewise the g-weight variance, the difference between the exhaustive and non-exhaustive form is the variance of the predictions $\hat{Y}_{0}(x)$ within the $s_{0,G}$ phase.

@@

\begin{subequations}\label{eq:pest_3p_synth_psynth_ext}
\begin{flalign}
\hat{\var}_{ext}(\hat{Y}_{G,extsynth,3p})&= \frac{1}{n_{1,G}(n_{2,G}-1)}\sum_{x\in{s}_{2,G}}
 (\hat{\mathbb{R}}_0(x)-\hat{\bar{\mathbb{R}}}_{0,G})^2 + 
 (1-\frac{n_{2,G}}{n_{1,G}})\frac{1}{n_{2,G}(n_{2,G}-1)}\sum_{x\in{s_{2,G}}}(\hat{\mathbb{R}}(x)-\bar{\hat{\mathbb{R}}}_G)^2 \label{eq:var_3p_reg_extsynth}&\\
\hat{\var}_{ext}(\hat{Y}_{G,extpsynth,3p})&= \frac{1}{n_{0,G}(n_{0,G}-1)}\sum_{x\in{s_{0,G}}}(\hat{Y}_0(x)-\hat{\bar{Y}}_{0,G})^2 + 
{\frac{1}{n_{1,G}(n_{2,G}-1)}\sum_{x\in{s}_{2,G}}}
 (\hat{\mathbb{R}}_0(x)-\bar{\hat{\mathbb{R}}}_{0,G})^2 \nonumber &\\
 &+ (1-\frac{n_{2,G}}{n_{1,G}})\frac{1}{n_{2,G}(n_{2,G}-1)}\sum_{x\in{s_{2,G}}}(\hat{\mathbb{R}}(x)-\bar{\hat{\mathbb{R}}}_G)^2 \label{eq:var_3p_reg_extpsynth}
\end{flalign}
\end{subequations}

with $\hat{Y}_{0}(x)=\pmb{\mathbb{Z}}^{(0)t}(x)\hat{\pmb{\gamma}}_{s_2}$ being the reduced model predictions and $\hat{\mathbb{R}}_{0}=Y(x)-\hat{Y}_{0}$ being the reduced model residuals. The equations for the point estimate and variances again look similar to the synthetic and pseudo synthetic form given in Eq. \ref{eq:pe_3p_synth}, \ref{eq:pe_3p_psynth}, \ref{eq:var_3p_reg_synth} and \ref{eq:var_3p_reg_psynth}. Note that they are however design-unbiased since the residual correction term is included in the regression coefficient vector $\hat{\pmb{\theta}}_{s_2}$.

>>>>

Solving the sample-based normal equations, the vector of regression coefficients $\hat{\pmb{\alpha}}_{s_2}$ for the \textbf{\textit{reduced model}}, i.e. using the \textit{reduced set of explanatory variables} $\pmb{Z}^{(0)}(x)$ available at $x \in s_0$, and likewise the vector of regression coefficients $\hat{\pmb{\beta}}_{s_2}$ for the \textbf{\textit{full model}}, i.e. using the \textit{full set of explanatory variables} $\pmb{Z}^t(x)=(\pmb{Z}^{(0)t}(x),\pmb{Z}^{(1)t}(x))$ available only at a subset $x \in s_1 \subset s_0$, are derived as

@@

The package allows for the calculation of \textbf{point estimates} under exhaustive and non-exhaustive use of the auxiliary information in the $s_0$ phase. Fitting the model using $s_2$ (i.e. \textit{internally}) ensures the zero mean residual property over $F$.

@@

In the \textit{non-exhaustive case}, the \textit{estimated} means of $\pmb{Z}^{(0)}(x)$ over both the $s_0$ and $s_1$ phase, as well as the \textit{estimated} mean of $\pmb{Z}(x)$ over the $s_1$ phase are calculated according to Eq. \ref{meanvalues3pnex}. If the exact mean over $s_0$ is known, the estimated mean $\hat{\bar{\pmb{Z}}}^{(0)}_0$ can simply be replaced by the exact mean $\bar{\pmb{Z}}^{(0)}_0$. Note that in case of applied boundary adjustment (Section \ref{sec:twophase_and_appl}), the simple mean is again replaced by the weighted mean analogous to Eq. \ref{eq:wmeanZ}.

@@

Note that $\hat{R}(x)=Y(x)-\pmb{Z}^t(x)\hat{\beta}_{s_2}$ denotes the residuals of the full model, whereas $\hat{R}_{0}(x)=Y(x)-\pmb{Z}^{(0)t}\hat{\alpha}_{s_2}$ denotes the residuals of the reduced model. The \textbf{external variance} form under linear regression models is defined as

\begin{subequations}\label{eq:extvar_reg3p}
\begin{align}
\hat{\var}_{ext}(\hat{Y}_{reg3p,ex})&=\frac{1}{n_1}\hat{\var}_{s_2}(\hat{R}_{0}(x)) + (1-\frac{n_2}{n_1})\frac{1}{n_2}\hat{\var}_{s_2}(\hat{R}(x))\label{eq:extvar_reg3p_ex} \\
\hat{\var}_{ext}(\hat{Y}_{reg3p,nex})&=\frac{1}{n_0}\hat{\var}_{s_0}(\hat{Y}_{0}(x))
+\frac{1}{n_1}\hat{\var}_{s_2}(\hat{R}_{0}(x)) + (1-\frac{n_2}{n_1})\frac{1}{n_2}\hat{\var}_{s_2}(\hat{R}(x)) \label{eq:extvar_reg3p_nex}
\end{align}
\end{subequations}
where $\hat{\var}_{s_0}$ indicates taking the sample variance over $s_0$.

@@

The three two-phase small area estimators described in Section \ref{sec:twophase_sae} can also be extended to the three-phase scenario. The general principle thereby stays the same, i.e. the regession coefficients of the reduced and full model and their variance-covariance matrices are calculated on the entire $s_2$ sample according to Eq. \ref{eq:normequ_redmod}, \ref{eq:normequ_fullmod}, \ref{eq:covar_alpha} and \ref{eq:covar_beta}, and are subsequently used to make predictions for sample locations restricted to small area $G$.

@@

The unbiased \textbf{point estimates} of the \textbf{small} (\textit{small}) and \textbf{pseudo small area estimator} (\textit{psmall}) are calculated by applying the globally derived reduced and full regression model coefficients to the small area means of the explanatory variables, and then correcting for a potential model bias in $G$ by adding the small area mean of the full model residuals, i.e. ${R}_{G}(x)=Y_G(x)-\pmb{Z}_G^t(x)\hat{\beta}_{s_2}$, to the point estimate. The difference between the mean $\hat{\bar{\pmb{Z}}}^{(0)}_{1,G}$ and the more precise or exact mean $\hat{\bar{\pmb{Z}}}^{(0)}_{0,G}$ and $\bar{\pmb{Z}}^{(0)}_{0,G}$ is again considered as a residual term likewise in the global estimation (Eq. \ref{eq:reg3p_ex} and \ref{eq:reg3p_nex}).

@@

\begin{subequations}\label{eq:pest_3p_small_psmall}
\begin{flalign}
\hat{\var}_{ext}(\hat{Y}_{G,small,3p})&= \frac{1}{n_{1,G}}\hat{\var}_{s_{2,G}}(\hat{R}_{0}(x)) + 
 (1-\frac{n_{2,G}}{n_{1,G}})\frac{1}{n_{2,G}}\hat{\var}_{s_{2,G}}(\hat{R}(x)) \label{eq:var_3p_reg_small}&\\
\hat{\var}_{ext}(\hat{Y}_{G,psmall,3p})&= \frac{1}{n_{0,G}}\hat{\var}_{s_{2,G}}(Y(x)) + (1-\frac{n_{1,G}}{n_{0,G}}) \frac{1}{n_{1,G}}\hat{\var}_{s_{2,G}}(\hat{R}_{0}(x)) \nonumber &\\
 &+ (1-\frac{n_{2,G}}{n_{1,G}})\frac{1}{n_{2,G}}\hat{\var}_{s_{2,G}}(\hat{R}(x)) \label{eq:var_3p_reg_psmall}
\end{flalign}
\end{subequations}
where $\hat{R}_{0}(x)=Y(x)-\hat{Y}_{0}(x)$ with $\hat{Y}_{0}(x)=\pmb{Z}^{(0)t}(x)\hat{\pmb{\alpha}}_{s_2}$. Likewise the g-weight variance, the difference between the exhaustive and non-exhaustive form is the variance of the predictions $\hat{Y}_{0}(x)$ within the $s_{0,G}$ phase.

@@

\begin{subequations}\label{eq:pest_3p_synth_psynth_ext}
\begin{flalign}
\hat{\var}_{ext}(\hat{Y}_{G,extsynth,3p})&= \frac{1}{n_{1,G}}\hat{\var}_{s_{2,G}}(\hat{\mathbb{R}}_{0}(x)) + 
 (1-\frac{n_{2,G}}{n_{1,G}})\frac{1}{n_{2,G}}\hat{\var}_{s_{2,G}}(\hat{\mathbb{R}}(x)) \label{eq:var_3p_reg_extsynth}&\\
\hat{\var}_{ext}(\hat{Y}_{G,extpsynth,3p})&= \frac{1}{n_{0,G}}\hat{\var}_{s_{2,G}}(Y(x)) + (1-\frac{n_{1,G}}{n_{0,G}}) \frac{1}{n_{1,G}}\hat{\var}_{s_{2,G}}(\hat{\mathbb{R}}_{0}(x)) \nonumber & \\
 &+ (1-\frac{n_{2,G}}{n_{1,G}})\frac{1}{n_{2,G}}\hat{\var}_{s_{2,G}}(\hat{\mathbb{R}}(x)) \label{eq:var_3p_reg_extpsynth}
\end{flalign}
\end{subequations}
where $\hat{\mathbb{R}}_{0}=Y(x)-\hat{\mathbb{Y}}_{0}(x)$ with $\hat{\mathbb{Y}}_{0}(x)=\pmb{\mathbb{Z}}^{(0)t}(x)\hat{\pmb{\gamma}}_{s_2}$. The equations for the point estimate and variances again look similar to the synthetic and pseudo synthetic form given in Eq. \ref{eq:pe_3p_synth}, \ref{eq:pe_3p_psynth}, \ref{eq:var_3p_reg_synth} and \ref{eq:var_3p_reg_psynth}. Just as in the two-phase context, they are design-unbiased since the residual correction term is included in the regression coefficient vector $\hat{\pmb{\theta}}_{s_2}$.
